Open source landscape ecology tools

### 2020-07-26 paper/paper.Rmd
adds maps creation references

All of the packages listed in Section \@ref(sec:spatrep) have build-in methods for plotting spatial data using the `plot()` function.
However, their defaults are focused on quick visual inspection of the data rather than the creation of complete maps.
Alternatively, the *mapview* package can be used for quick interactive visualization of spatial data.
The *tmap* package provides a coherent plotting system for static and interactive maps that is based on the layered grammar of graphics \cite{Tennekes2018}.
This package aims for creating publication-ready maps.
Both, *tmap* and *mapview* build upon the *leaflet* package and leaflet javascript library.<!--this sentence can be easily removed-->
R's general-purpose plotting package *ggplot2* together with its extension *ggspatial* also offers some capabilities for plotting spatial data.

>>>>

All of the packages listed in Section \@ref(sec:spatrep) have build-in methods for plotting spatial data using the `plot()` function.
However, their defaults are focused on quick visual inspection of the data rather than the creation of complete maps.
Alternatively, the *mapview* package can be used for quick interactive visualization of spatial data \cite{R-mapview}.
The *tmap* package provides a coherent plotting system for static and interactive maps that is based on the layered grammar of graphics \cite{Tennekes2018}.
This package aims for creating publication-ready maps.
Both, *tmap* and *mapview* build upon the *leaflet* package and leaflet javascript library \cite{R-leaflet}.<!--this sentence can be easily removed-->
R's general-purpose plotting package *ggplot2* together with its extension *ggspatial* also offers some capabilities for plotting spatial data \cite{Wickham2016a,R-ggspatial}.
